Verifying Demonstrations

### 2018-08-16 paper/DB-anon-cred.tex
Breaks DB-Schnorr out into its own section

\subsection{Distance-bounding anonymous credentials}%
\label{DB-anon-cred}

@@

\emph{Reattempting a distance-bounding Schnorr protocol.}
In the original \ac{DB} paper by \citet{DistanceBounding}, one of the distance-bounding protocol is based on the Schnorr identification scheme~\cite{Schnorr}.
However, this \ac{DB} Schnorr protocol was shown to be prone to distance hijacking~\cite{DistanceHijacking}, in addition to not being secure against terrorist fraud.
We now propose another way to turn the Schnorr protocol into a
public-key \ac{DB} protocol which is secure against \ac{DBMF},
\ac{DBDF}, \ac{DBDH} and \ac{DBTF}.
The public-key property implies protection against an impersonating
verifier.
\sonja{Contrast with \ac{DBIF}}

@@

>>>>

\section{Distance-bounding anonymous credentials}%
\label{DB-anon-cred}

@@

\subsection{Reattempting a distance-bounding Schnorr protocol}

In the original \ac{DB} paper by \citet{DistanceBounding}, one of the distance-bounding protocol is based on the Schnorr identification scheme~\cite{Schnorr}.
However, this \ac{DB} Schnorr protocol was shown to be prone to distance hijacking~\cite{DistanceHijacking}, in addition to not being secure against terrorist fraud.
We now propose another way to turn the Schnorr protocol into a
public-key \ac{DB} protocol which is secure against \ac{DBMF},
\ac{DBDF}, \ac{DBDH} and \ac{DBTF}.
The public-key property implies protection against an impersonating
verifier.
\sonja{Contrast with \ac{DBIF}}

@@

\subsection{Security analysis}
